The globular cluster system of the Auriga simulations

### 2019-08-18 AurigaGCS.tex
Updated Figure 9 for #1

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold-trim}.png}
    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold-trim}.png}
    \caption{
        The top (bottom) panel shows the logarithm of the ratio of simulated mass
        to mass in the MW (M31) GCS, i.e. the logarithm of the mass ratio. The
        number in each bin shows the color-coded value that is plotted, and the
        (median) star particle count is given in parenthesis. Note that the three 
        bins in the upper right corner are left blank because the observations
        have zero mass there.
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold_diverging-trim}.png}
    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold_diverging-trim}.png}
    \caption{
        The top (bottom) panel shows the logarithm of the ratio of simulated mass
        to mass in the MW (M31) GCS, i.e. the logarithm of the mass ratio, minus
        the median value. This way red indicates regions of with a higher mass
        excess than the median, conversely blue highlights bins with a lower than
        median mass ratio. The number in each bin shows the color-coded value 
        that is plotted, and the (median) star particle count is given in 
        parenthesis. Note that the three bins in the upper right corner are white
        because the observations have zero mass there.
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}

### 2019-08-18 AurigaGCS_20190802.tex
Updated Figure 9 for #1

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold-trim}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold-trim}.png}
    \caption{
        The top (bottom) panel shows the logarithm of the ratio of simulated mass
        to mass in the MW (M31) GCS, i.e. the logarithm of the mass excess. The
        color-coded values are also shown in each bin. Note that the three bins
        in the upper right corner are left blank because the observations have
        zero mass there, and that the numbers indicate how much (median) mass is
        produced by the simulations in those bins.
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold_diverging-trim}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold_diverging-trim}.png}
    \caption{
        The top (bottom) panel shows the logarithm of the ratio of simulated mass
        to mass in the MW (M31) GCS, i.e. the logarithm of the mass excess. The
        color-coded values are also shown in each bin. Note that the three bins
        in the upper right corner are left blank because the observations have
        zero mass there, and that the numbers indicate how much (median) mass is
        produced by the simulations in those bins.
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}
